%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Manager of Engineering} % Job title
    {Conga} % Organization
    {Broomfield, CO} % Location
    {Aug. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed and executed new-hire program focused on increasing DE\&I within engineering, resulting in 100\% increase in BIPOC and gender diverse team members.}
      \item {Reduced Cloud spend by \$100k annually, increased reliability, and aligned Conga Cloud strategy by migrating legacy monolith from PaaS to AWS and containerizing it for use with Kubernetes. Led as project manager and lead engineer.}
      \item {Eliminated misaligned commitment deliveries for complex customer workflows by introducing MVP scoping process to product organization with 100\% adoption rate.}
	\item {Led three engineering teams (19 distributed direct reports) to grow and transform Conga's flagship product, Composer; \$125MM ARR, 12k customers, 500k seats.}
	\item {Mitigated \$20MM ARR impact by mobilizing engineering organization in response to critical subprocessor end-of-life. Ran project end-to-end for suite of new microservices including all aspects from vendor negotiation to requirements gathering, implementation, integration, testing, deployment, and support plan.}
	\item {Reduced recurring engineering spend by \$250k transitioning three products into maintenance, creating off-shore support team and product transition model to optimize cost, and enabling senior on-shore staff to focus on innovation rather than maintenance.}
      \end{cvitems}
    }

  \cventry
    {Staff Software Engineer, Team Lead} % Job title
    {} % Organization
    {} % Location
    {Sept. 2016 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Co-led greenfield effort to design, build, and deploy at scale C\#/.NET microservices-based product offering consisting of polyglot stack and Infrastructure as Code (IaC) tooling.}
        \item {Retained two \$1MM ARR client accounts and achieved 70\% performance gain by introducing dynamic analysis practices and customer-facing plan to address application performance issues.}
%        \item {Developed auto-generating UML-based sequence diagramming system to document complex microservices interactions.}
        \item {Led as a senior member of an Agile, product-driven Ruby on Rails engineering team to consistently deliver robust features, bug-fixes, and thought leadership.}
        \item {Enabled acquisition of start-up Octiv by Conga through discovery and mitigation of legal and licensing risks.}
      \end{cvitems}
    }
    
%  \cventry
%  {Agile Team Lead} % Job title
%  {Trilogy Education Services} % Organization
%  {New York, NY} % Location
%  {Sept. 2019 - Jan. 2020} % Date(s)
%  {
%    \begin{cvitems} % Description(s) of tasks/responsibilities
%      \item {Coached students through 8-week industry-like Agile project to develop team skills and technical proficiency.}
%      \item {Aided students in technical scoping, programming, and quality assurance tasks.}
%      \item {Prepared lesson plans and demonstrations to fill gaps in course materials.}
%    \end{cvitems}
%  }

    \cventry
      {Leadership Program- Program Management \& Engineering} % Job title
      {GE Aviation Systems} % Organization
      {Grand Rapids, MI} % Location
      {Aug. 2013 - Aug. 2016} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Successfully led customer interactions with key programs resulting in \$6MM+ in sales and ungrounding of military aircraft fleets.}
          \item {Assembled and led cross-functional team of 15 through manufacturing readiness review, transitioning \$23MM program into production.}
          %\item {Recommended and implemented cost-saving configuration management procedures for 40 person team.}
          %\item {Owned software integration of entire program, identified and resolved issues ranging from kernel to application code.}
          %\item {Independently authored cost-saving verification tooling that was fully adopted by the verification team.}
          %\item {Led and participated in formal reviews of certification and planning documents.}
	  \item {Created and executed the largest grassroots cross-site professional development event in GE's 100+ year history as board member for the Early Career Professionals Organization affinity group.}
        \end{cvitems}
      }

      \cventry
        {Lead Developer} % Job title
        {Study Abroad, Michigan State University} % Organization
        {East Lansing, MI} % Location
        {Jul. 2009 - Aug. 2013} % Date(s)
        {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Sole developer for second-largest Study Abroad program in the United States; PHP, Zend Framework.}
          \end{cvitems}
        }
%---------------------------------------------------------
\end{cventries}
